%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Original author:
% Sapna Gulati (http://sapnagulati.net)
%
% Original repository:
% https://github.com/SapnaGulati
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[]{sapna-resume}


\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.33\textwidth} 
\begin{large}
	\headername{Sapna}\\
\end{large}
\vspace{3pt}
Final Year (B.Tech)\\
Computer Science $\&$  Engineering\\ 
at SSIET,Jalandhar. \\ 
SGPA:8.573 till 6th Sem 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     LINKS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Links} 
\noindent\rule{5cm}{0.4pt}

Github:// \href{https://github.com/SapnaGulati}{\custombold{SapnaGulati}} \\
LinkedIn:// \href{https://www.linkedin.com/in/sapna-gulati-5a44ba19a}{\custombold{SapnaGulati}}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Skills}
\noindent\rule{5cm}{0.4pt}
\subsection{OS}
Windows, Linux
\vspace{6pt}
\subsection{Languages}
C/C++, Java, Python, \\ Basic Level: Kotlin, C\#, Git, HTML
\vspace{6pt}
\subsection{Framework}
Android Development, \\GUI Development,
\\Basic Web Development
\vspace{6pt}
\subsection{Databases}
SQL, MySQL, SQLite
\vspace{6pt}
\subsection{Others}
GitHub, Git,\\Sublime Text, Eclipse, NetBeans\\
Android Studio,\\PyChram, VS Code, \\Visual Studio.
\sectionsep
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     COURSEWORK
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Coursework}
\noindent\rule{5cm}{0.4pt}

Android Development\\
GUI Development\\
Data Structures\\
Algorithm\\
Operating Systems\\
MySQL\\
Basic Data Analysis
\sectionsep
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Education} 
\noindent\rule{5cm}{0.4pt}\\
\datecolor{2017-2021}
\subsection{B.Tech(CSE)}
SSIET, Jalandhar. \\
SGPA : 8.7/10(Expected)\\
\vspace{8pt}
\datecolor{completed in 2017}
\subsection{12th(Non-Medical)}
Shiv Jyoti Public School, Jalandhar.\\
\vspace{8pt}
\sectionsep
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{minipage} 
\hfill
\begin{minipage}[t]{0.66\textwidth} 
% \descript{B-Tech in Computer Science}
\hspace*{0pt}\hfill    \\
\hspace*{0pt}\hfill    \\
\hspace*{0pt}\hfill Jalandhar, Punjab. \\
\hspace*{0pt}\hfill Mob.: +91-9876061473 \\
\hspace*{0pt}\hfill Email.:\textbf{\href{mailto:sapnagulati9990@gmail.com}{sapnagulati9990@gmail.com}}  
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     PROJECTS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Projects}
\noindent\rule{12.5cm}{0.4pt}
\datecolor{July,2019-Now} \runsubsection{Java GUI Project}
\descript{Slide AND Double Just 12}
\noindent
\hspace{5em}%
\begin{minipage}{0.85\textwidth\vspace{2pt}}
Slide AND Double is game in which two numbers when slide they will get merged into double of that number if both the numbers are same. It will go up-to 4096 i.e. 2$^1^2$.
\end{minipage}
\descriptright{(Java and MySQL)}
\sectionsep

\datecolor{November,2020-Now} \runsubsection{Python GUI Project}
\descript{Flappy Bird Game}
\noindent
\hspace{5em}%
\begin{minipage}{0.85\textwidth\vspace{2pt}}
Flappy Bird is a game which is developed using python language of a bird which is flapping in between the pipes and will die when strikes with the upper and lower pipes or the upper and lower edge of the screen.
\end{minipage}
\descriptright{(Python)}
\sectionsep

\datecolor{September,2020-Now} \runsubsection{Android Game}
\descript{Tic Tac Toe}
\noindent
\hspace{5em}%
\begin{minipage}{0.85\textwidth\vspace{2pt}}
Tic Tac Toe is a game which can be run on all android mobiles.
\end{minipage}
\descriptright{(Java and XML)}
\sectionsep

\datecolor{October,2020-Now} \runsubsection{College App}
\descript{College App}
\noindent
\hspace{5em}%
\begin{minipage}{0.85\textwidth\vspace{2pt}}
College app is a project developed specifically for the college purpose. In which, there are two apps- one is for the faculty members in which they can upload images, e-books and notices etc. the other one is for the students in which they can see all the data uploaded by the faculty members.
\end{minipage}
\descriptright{(Android, Google map, Java, Fire-base Database)}
\sectionsep

\datecolor{July,2019-Now} \runsubsection{Java QUIZ Project}
\descript{Brain Booster}
\noindent
\hspace{5em}%
\begin{minipage}{0.85\textwidth\vspace{2pt}}
Brain booster is a quiz game for guessing the right spelling of the word and after that meaning can be seen.
\end{minipage}
\descriptright{(Java and MySQL)}
\sectionsep

\datecolor{July,2019-Now} \runsubsection{Android App}
\descript{Social App}
\noindent
\hspace{5em}%
\begin{minipage}{0.85\textwidth\vspace{2pt}}
Social App is a app just like social media apps. Functionality of sign-in using google is implemented. Fire-base data uploading along with data fetching concept is used in this app.
\end{minipage}
\descriptright{(Java, XML and Fire-base database)}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     CERTIFICATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Certification} 
\noindent\rule{12.5cm}{0.4pt}
\datecolor{June 2019} \runsubsection{Solitaire Infosys, Mohali.}
\descript{2 month Training}
\noindent
\hspace{5em}%
\begin{minipage}{0.85\textwidth\vspace{2pt}}
In this training, "Brain Booster" and "Slide AND Double Just 12", two games was developed.
\end{minipage}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     OTHER ACTIVITIES
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Other Achievements} 
\noindent\rule{12.5cm}{0.4pt}
\hspace{5em}%
\begin{minipage}{0.85\textwidth\vspace{2pt}}
- Participated in tech fest organized in campus.
\end{minipage}
\begin{minipage}{0.85\textwidth\vspace{2pt}}
- Self Learned Python and Android Development. 
\end{minipage}
\begin{minipage}{0.85\textwidth\vspace{2pt}}
- Class Representative from last 3 years. 
\end{minipage}
\begin{minipage}{0.85\textwidth\vspace{2pt}}
- Extra Curricular Activities: Listening Music, Playing Badminton, Developing Games for fun and knowledge.
\end{minipage}
    
\end{minipage} 
\end{document}  \documentclass[]{article}
